### 2024-05-28 README.Rmd
New top-level README file

---
title: ""
output: 
  html_document:
    template: ../assets/template.html
    css: ../assets/style.css
editor_options: 
  markdown: 
    wrap: sentence
---

## Data {#data}

@@

>>>>

---
title: ""
output: 
  html_document:
    template: assets/template.html
    css: assets/style.css
    keep_md: true
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=F, echo=F}
library(tidyverse)
library(glue)
devtools::load_all("D:/repositories/projectlog")
#source('scripts/dependencies.R')

knitr::opts_chunk$set("ft.shadow" = FALSE, echo = F, message = F, warning = F)

```
<br>
This repository contains data, code, and output for a project entitled "Childhood adversity is not associated with lowered inhibition, but lower perceptual processing: A Drift Diffusion Model analysis". The manuscript is currently under review at *Cognitive Development*.

Do you want to download or clone the materials for this project? Go to [https://github.com/stefanvermeent/attention_project](https://github.com/stefanvermeent/attention_project).

## Directory Structure {#structure}

The names of each folder are intended to be self-explanatory.
There are eight top-level folders to organize the inputs and outputs of this project:

1.  [`Manuscript`](https://stefanvermeent.github.io/attention_project/manuscript/README.html): The Registered Report written in Quarto.
2.  [`Supplement`](https://stefanvermeent.github.io/attention_project/supplement/README.html): a supplemental text (to be submitted with the manuscript) documenting all secondary analyses in detail.
3.  [`Preregistrations`](https://stefanvermeent.github.io/attention_project/preregistrations/README.html): Contains a sub-folder for each study, which in turn contain all scripts, materials, analysis objects, and preregistration documents for that study (see below for more information).
4.  [`Data`](https://stefanvermeent.github.io/attention_project/data/README.html): Contains a sub-folder for each study, which in turn contain all raw and processed data files needed to reproduce the results.

Click on each of the folders to get more details.

## Overview of project milestones

Below is an overview of all the project milestones, such as first-time data access, submissions, and revisions.
Data access events were automatically captured using custom code, which over the course of this project was collected in the R package `projectlog` [https://stefanvermeent.github.io/projectlog/](https://stefanvermeent.github.io/projectlog/).
For more information about how tracking worked, Go to the [Open science workflow tab](https://stefanvermeent.github.io/abcd_ddm/opensci_workflow/README.html).

```{r results ='asis', echo = FALSE}
milestones <- gert::git_tag_list() |> 
  mutate(
    tags = pmap(list(name = name, ref = ref, commit = commit), function(name, ref, commit) {
      gert::git_commit_info(commit) |> 
        as_tibble() |> 
        select(commit = id, author, time, message) 
    })
  ) |> 
  select(-commit, -ref) |> 
  unnest(tags) |> 
  separate(message, into = c("description", "hash", "code"), sep = "\\n") |> 
  mutate(
    name = map_chr(name, function(name) {
      name |> 
        str_remove("\\[\\[") |>
        str_remove("\\d*$") |> 
        str_replace("_", " ") |> 
        str_to_title()
    })
  ) |> 
  mutate(
    code = str_remove_all(code, "^code\\s") |> str_replace_all(string = _, "\\|\\>", "\\|\\>\\\n"),
    link_to_git = paste0(
       gert::git_remote_list()$url |> str_remove(string = _, pattern = "\\.git$"), "/tree/", commit)
    ) |>
  arrange(desc(time))

# Write scripts including code to .projectlog folder
milestones |> 
  pwalk(function(name,commit,author,time,description,hash,code,link_to_git){

    if(name == "Data Access"){
      code <- code |> 
        str_replace_all(string = _, "\\|> ", "\\|>\n") |> 
        str_remove(string = _, "^code ")

      url <- gert::git_remote_list()$url |> 
        str_remove(string = _, "\\.git$") |> 
        paste0(paste0("/commit/", commit))

      #  url <- "<anonymized repository>"

      script <-
        glue(
          "
          ### Date: {time}\n
          ### Description: {description}\n\n
          ### For more information on this commit, see the README file, or go to {url}\n
          ### Below is the full code that was used to access the data:\n\n
          {code}"
        )

      writeLines(script, con = paste0(".projectlog/", commit, ".R"))
    }
  })

branch <- gert::git_branch_list() |> filter(local == TRUE) |> pull(name)

# Print milestones
glue_data(milestones, "  - **[{time}]({link_to_git}): {description}**
        - **Milestone:** {name}
        - **Data MD5 hash**: {hash}
        - [Link to code snippet](https://github.com/StefanVermeent/liss_wm_profiles_2023/blob/{branch}/.projectlog/{commit}.R)
        \n
    ")

```

## How to reproduce this repository {#reproduce}

@@

### Contact

For questions or comments, feel free to contact me at p.c.s.vermeent@gmail.com.
